Quantifying the Importance of Change for Understanding Differences in Personal Culture

### 2024-03-22 manuscript/manuscript.Rmd
data note

>>>>

# Data Note

This paper uses unit record data from Household, Income and Labour Dynamics in Australia Survey [HILDA] conducted by the Australian Government Department of Social Services (DSS). The findings and views reported in this paper, however, are those of the authors and should not be attributed to the Australian Government, DSS, or any of DSS’ contractors or partners. DOI: 10.26193/0LPD4U. The SOEP is administered at the German Institute for Economic Research (DIW Berlin) and funded by the Federal Ministry for Education and Research (BMBF) and the state governments under the umbrella of the Leibniz Association. The BHPS data were made available through the UK data archive. The data were originally collected by the ESRC research center on micro-social change at the University of Essex, now incorporated within the Institute for Social and Economic Research. The authors bear full responsibility for the analyses and interpretation of the data presented in this article. Understanding Society is an initiative funded by the Economic and Social Research Council and various Government Departments, with scientific leadership by the Institute for Social and Economic Research, University of Essex, and survey delivery by NatCen Social Research and Kantar Public. The research data are distributed by the UK Data Service. This study has been realized using data collected by the Swiss Household Panel (SHP), which is based at the Swiss Centre of Expertise in the Social Sciences FORS. The project is supported by the Swiss National Science Foundation. This study also uses data from The General Social Survey (GSS), which is a project of the independent research organization NORC at the University of Chicago, with principal funding from the National Science Foundation. The collection of data used in the PSID was partly supported by the National Institutes of Health under grant number R01 HD069609 and R01 AG040213, and the National Science Foundation under award numbers SES 1157698 and 1623684.

### 2024-03-22 manuscript/manuscript.tex
data note

>>>>

\hypertarget{data-note}{%
\section{Data Note}\label{data-note}}

This paper uses unit record data from Household, Income and Labour
Dynamics in Australia Survey {[}HILDA{]} conducted by the Australian
Government Department of Social Services (DSS). The findings and views
reported in this paper, however, are those of the authors and should not
be attributed to the Australian Government, DSS, or any of DSS'
contractors or partners. DOI: 10.26193/0LPD4U. The SOEP is administered
at the German Institute for Economic Research (DIW Berlin) and funded by
the Federal Ministry for Education and Research (BMBF) and the state
governments under the umbrella of the Leibniz Association. The BHPS data
were made available through the UK data archive. The data were
originally collected by the ESRC research center on micro-social change
at the University of Essex, now incorporated within the Institute for
Social and Economic Research. The authors bear full responsibility for
the analyses and interpretation of the data presented in this article.
Understanding Society is an initiative funded by the Economic and Social
Research Council and various Government Departments, with scientific
leadership by the Institute for Social and Economic Research, University
of Essex, and survey delivery by NatCen Social Research and Kantar
Public. The research data are distributed by the UK Data Service. This
study has been realized using data collected by the Swiss Household
Panel (SHP), which is based at the Swiss Centre of Expertise in the
Social Sciences FORS. The project is supported by the Swiss National
Science Foundation. This study also uses data from The General Social
Survey (GSS), which is a project of the independent research
organization NORC at the University of Chicago, with principal funding
from the National Science Foundation. The collection of data used in the
PSID was partly supported by the National Institutes of Health under
grant number R01 HD069609 and R01 AG040213, and the National Science
Foundation under award numbers SES 1157698 and 1623684.
